Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-17 text/paper2/ms.tex
switch to lnR

In \paperone, we define a set of coordinates relative to the instantaneous phase-space position of the progenitor, $(\bs{r}_{p},\bs{v}_{p})$, normalized by the instantaneous tidal radius and escape velocity. Here we (1) instead scale the velocity coordinates by the velocity dispersion of the satellite, (2) reduce the dimensionality by considering only the magnitude of these vectors, and (3) take the logarithm of the magnitude,
\begin{equation}
  R = \ln\left(\frac{\left\vert\bs{r} - \bs{r}_{p}\right\vert}{R_{\rm tide}}\right)\,\,\,\,,\,\,\,\,
  V = \ln\left(\frac{\left\vert\bs{v} - \bs{v}_{p}\right\vert}{\sigma_v}\right).
\end{equation}
Figure~\ref{fig:R_V} shows distributions of $R$ and $V$ --- computed at $t=t_{\rm ub}$ for each particle --- as a function of progenitor mass from the simulations described in Section~\ref{sec:sims}. In these scaled, log coordinates we model distributions in $R$ and $V$ as Gaussians. We find that for masses $\lesssim10^9M_\odot$, the variance ($\sigma^2$ in plot panels) remains approximately constant and the mean stays fixed at 0. For the largest mass simulation ($2.5\times10^9M_\odot$), the perturbation to the total potential due to the progenitor halo becomes significant and thus a large fraction of the stars are disrupted through interactions with the subhalo. For this article, we ignore covariances between $R$ and $V$. The

@@

[Cold vs. Hot streams in the context of observational errors]

>>>>

In \paperone, we define a set of coordinates relative to the instantaneous phase-space position of the progenitor, $(\bs{r}_{p},\bs{v}_{p})$, normalized by the instantaneous tidal radius and escape velocity. Here we (1) instead scale the velocity coordinates by the velocity dispersion of the satellite, (2) reduce the dimensionality by considering only the magnitude of these vectors, and (3) take the logarithm of the magnitude,
\begin{equation}
  \ln R = \ln\left(\frac{\left\vert\bs{r} - \bs{r}_{p}\right\vert}{R_{\rm tide}}\right)\,\,\,\,,\,\,\,\,
  \ln V = \ln\left(\frac{\left\vert\bs{v} - \bs{v}_{p}\right\vert}{\sigma_v}\right).
\end{equation}
Figure~\ref{fig:R_V} shows distributions of $\ln R$ and $\ln V$ --- computed at $t=t_{\rm ub}$ for each particle --- as a function of progenitor mass from the simulations described in Section~\ref{sec:sims}. In these scaled coordinates we model distributions in $R$ and $V$ as log-normal and ignore covariances between $R$ and $V$. We find that for masses $\lesssim10^9M_\odot$, the variance ($\sigma^2$ in plot panels) remains approximately constant and the mean stays fixed at 0. For the largest mass simulation ($2.5\times10^9M_\odot$), the perturbation to the total potential due to the progenitor halo becomes significant and thus a large fraction of the stars are disrupted through interactions with the subhalo.

@@

The scale-radius and velocity dispersion scale with the mass of the progenitor. [...observational errors] [ $D_{\rm ps}$]
[Cold vs. Hot streams in the context of observational errors]

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{../../plots/paper2/num_recombine.png}
\caption{ TODO }\label{fig:R_V}
\end{center}
\end{figure}
